Revisited hidden weight bit function

### 2024-10-29 RevisedHiddenWeight.tex
Added more bounds for different t

%\begin{definition}[Algebraic Immunity] \label{def:ai}
%	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
%	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
%	where $\degg(g)$ is the algebraic degree of $g$.
%	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
%	Additionally we denote $\AN(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0\}$.
%\end{definition}
\begin{definition}[Nonlinearity %and weightwise nonlinearity
	] \label{def:nl}
	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$, where $n$ is a positive integer, is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
	\[ \NL(f) = \min_{g,\, \degg(g)\leq 1} \{ \hd(f,g) \}{,} \]
	where $g(x)=a\cdot x+\varepsilon$, $a\in \F_2^n, \varepsilon\in \F_2$. 	
	The nonlinearity can also be defined from the Walsh transform:
	\[ \NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}. \]
\end{definition}

@@

\begin{Prop}[\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
    Let $w$ be a complex number, and let $R>0$ be some radius. If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
    \[
        \left|\frac{\dd^k}{\dd^k z}f(w)\right|\leq\frac{k!\cdot M_R}{R^k},
    \]
    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
\end{Prop}

@@

\begin{proposition}
    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
    \[
        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
    \]
\end{proposition}

@@

>>>>

%\begin{definition}[Algebraic Immunity] \label{def:ai}
%	The algebraic immunity of a Boolean function $f\in \Bfn{n}$, denoted as $\AI(f)$, is defined as:
%	\[ \AI(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0 \; \text{or} \; (f + 1)g = 0 \}{,} \]
%	where $\degg(g)$ is the algebraic degree of $g$.
%	The function $g$ is called an annihilator of $f$ (or $f + 1$). 
%	Additionally we denote $\AN(f) = \min_{g \neq 0}\{ \degg(g) \; | \; fg = 0\}$.
%\end{definition}
\begin{definition}[Nonlinearity]%and weightwise nonlinearity
	\label{def:nl}
	The nonlinearity $\NL(f)$ of a Boolean function $f\in \BN$, where $n$ is a positive integer, is the minimum Hamming distance between $f$ and all the affine functions in $\BN$:
	\[ \NL(f) = \min_{g,\, \degg(g)\leq 1} \{ \hd(f,g) \}{,} \]
	where $g(x)=a\cdot x+\varepsilon$, $a\in \F_2^n, \varepsilon\in \F_2$. 	
	The nonlinearity can also be defined from the Walsh transform:
	\[ \NL(f) = 2^{n-1}- \frac{1}{2} \max_{a\in \F_2^n}{|\wt{f}(a)|}. \]
\end{definition}

@@

\begin{Prop}[\cite{rudin1987}, Theorem 10.26]\label{property:cauchy_estimate}
    Let $w$ be a complex number, and let $R>0$ be some radius. If $f$ is a holomorphic function defined on an open set containing every complex number $z$ satisfying $|z-w|<R$, then for every integer $k\geq 0$, the $k$-th derivative of $f$ evaluated at $w$ can be bounded, in absolute value, as follows:
    \[
        \left|\frac{\dd^k}{\dd^k z}f(z)\vert_{z=w}\right|\leq\frac{k!\cdot M_R}{R^k},
    \]
    where $M_R$ is the maximum of $|f(z)|$ on the circle $|z-w|=R$.
\end{Prop}

@@

\begin{proposition}\label{proposition:walsh_t_over_3}
    Let $n\in\N$ be divisible by $6$. Then for every $a\in\F_2^n$ and every $k\in[0,n]$, it holds that:
    \[
        |\wtk{d_{n/3,n}}{k}(a)|\leq2^{3n/4},\quad|\wt{d_{n/3,n}}(a)|\leq 1+n\cdot 2^{3n/4}.
    \]
\end{proposition}

@@

\begin{remark}
    The proof of Proposition~\ref{proposition:walsh_t_over_3} can be redone for other values of $t$. In Figure~\ref{fig:walsh_bounds_generalization}, we provide bounds of the form $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$, where $\alpha\in[0,20]$ is represented on the $x$-axis and $\beta$ is represented on the $y$-axis. 
\end{remark}

\begin{figure}
	\centering
	\includegraphics[width=9cm]{walsh_bounds_generalization.pdf}
	\caption{For each point $(\alpha,\beta)$, we have $\max_{a\in\F_2^n}|\wt{d_{\alpha n/40,n}}(a)|\leq 1+n\cdot 2^{\beta n}$.}
    \label{fig:walsh_bounds_generalization}
\end{figure}
